Imperative Programming with Variational Effects

### 2018-08-08 paper/paper.tex
styling; abstract

\documentclass[letterpaper,10pt,onecolumn]{article}

\usepackage{setspace} 
\singlespacing
\usepackage{graphicx}                                        
\usepackage{amssymb}                                         
\usepackage{amsmath}                                         
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{algorithmic}
\usepackage{url}
\usepackage{tikz}         
\usetikzlibrary{matrix}
\usepackage{listings}
\usepackage{tabu}
\usepackage{mathptmx}
\usepackage{fullpage}
\usepackage{enumerate}
\usepackage{fancyvrb}
\usepackage{mathpartir}
\usepackage{lambda}
\usepackage{cc}
\usepackage{cc-ext}
\usepackage{alltt}
\usepackage{textcomp}

%%%
%%% Formatting details
%%%
\sloppy
\sloppypar
\widowpenalty=0
\clubpenalty=0
\displaywidowpenalty=0
\raggedbottom
\pagestyle{plain}

@@

\usepackage{listings}

@@

\usepackage{geometry}
\geometry{textheight=9.5in, textwidth=7in}
\parindent = 0.0 in
\parskip = 0.1 in
\title{Imperative Programming with Variational Effects}
\author{Alex Grasley}
\begin{document}

@@

\section{Introduction}
\label{ch:intro}

@@

\section{Background}
\label{ch:bg}

\subsection{The choice calculus}

@@

\subsection{Implementation of Formula Trees}

@@

\subsection{Properties of choices}

@@

\section{Motivation}
\label{ch:mot}

@@

\subsection{Pure variational execution}

@@

\subsection{Mutable State}

@@

\subsection{Exceptions}

@@

\subsection{Comparison with Existing Work}

@@

\section{IMP}

@@

\section{Variational IMP with Effects}

@@

\subsection{Variational Operations}

@@

\subsection{Variational Context and Variational Store}

@@

\section{The Resource DSL}

@@

\subsection{Resources}

@@

\subsection{Expressions}

@@

\subsection{Effects on Resources}

@@

\subsection{Statements}

>>>>

\documentclass[onehalf,11pt]{beavtex}

\usepackage{amssymb}                                         
\usepackage{amsmath}                                         
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{algorithmic}
\usepackage{url}
\usepackage{tikz}         
\usetikzlibrary{matrix}
\usepackage{listings}
\usepackage{tabu}
\usepackage{mathptmx}
\usepackage{fullpage}
\usepackage{enumerate}
\usepackage{fancyvrb}
\usepackage{mathpartir}
\usepackage{lambda}
\usepackage{cc}
\usepackage{cc-ext}
\usepackage{alltt}
\usepackage{textcomp}

@@

@@

\title{Imperative Programming with Variational Effects}
\author{Alex Grasley}
\degree{Master of Science}
\doctype{Thesis}
\department{Electrical Engineering and Computer Science}
\depttype{School}
\depthead{Director}
\major{Computer Science}
\advisor{Eric Walkingshaw}
\submitdate{August 27, 2018}
\commencementyear{2018}
\abstract{
Variation is a commonly encountered element of modern software systems.
One area in which variation is frequently encountered is in defining
configurations and resource requirements for the deployment of such
systems. To this end, we have developed the Resource DSL, a language that aids in the specification
of resource requirements for highly configurable software systems.
In the Resource DSL,
variation is a first-class language construct.
This permits the efficient checking of many possible configurations against
a set of resource requirements.

During development of the Resource DSL, we encountered a number of
difficulties in the interaction of variation and side effects. Previous variational
languages have encountered similar issues and have developed a range of
techniques to address them. This thesis builds upon this work
and provides a formal operational semantics for a simple imperative language
that includes both variation and side effects. After presenting this formalization,
we demonstrate how it is successfully applied in our work on the Resource DSL.
}
\acknowledgements{
TODO
}

\begin{document}

@@

\mainmatter

\chapter{Introduction}
\label{ch:intro}

@@

\chapter{Background}
\label{ch:bg}

\section{The choice calculus}

@@

\section{Implementation of Formula Trees}

@@

\section{Properties of choices}

@@

\chapter{Motivation}
\label{ch:mot}

@@

\section{Pure variational execution}

@@

\section{Mutable State}

@@

\section{Exceptions}

@@

\section{Comparison with Existing Work}

@@

\chapter{IMP}
\label{ch:imp}

@@

\chapter{Variational IMP}
\label{ch:vimp}

@@

\section{Variational Operations}

@@

\section{Variational Context and Variational Store}

@@

\chapter{The Resource DSL}
\label{ch:rdsl}

@@

\section{Resources}

@@

\section{Expressions}

@@

\section{Effects on Resources}

@@

\section{Statements}
